How do families shape average neighbourhood incomes in Toronto?

### 2024-12-04 paper/paper.qmd
fixed format of overall pdf
updated paper with title and subtitle

---
title: "..."
subtitle: "..."
author: 
  - Julia Lee
thanks: "Code and data are available at: https://github.com/jjlee-lee/Toronto_Neighbourhood_Income.git"
date: today
date-format: long
abstract: "By examining Toronto Neighbourhood Profiles data, the following analysis aims to understand what kinds of families drive average neighbourhood income to help support planning decisions for individual neighbourhoods along with local and general businesses. With both data visualization and the application of a linear regression model, this analysis finds that 2-person and 4-person families are key drivers of average neighbourhood income throughout Toronto. This implies that focusing neighbourhood or business planning decisions on these types of families may help to increase a neighbourhood or business’ income position. Further, this analysis highlights that additional considerations for the unique characteristics of these key driver families are important to understand the interplay between families and neighbourhood income in more depth."
format: pdf
number-sections: true
bibliography: references.bib
---

@@

>>>>

---
title: "How do families shape average neighbourhood incomes in Toronto?"
subtitle: "Different family sizes appear to impact income in different ways with 2 and 4-person families being key drivers of average neighbourhood incomes in Toronto"
author: 
  - Julia Lee
thanks: "Code and data are available at: https://github.com/jjlee-lee/Toronto_Neighbourhood_Income.git"
date: today
date-format: long
abstract: "By examining Toronto Neighbourhood Profiles data, the following analysis aims to understand what kinds of families drive average neighbourhood income to help support planning decisions for individual neighbourhoods along with local and general businesses. With both data visualization and the application of a linear regression model, this analysis finds that 2-person and 4-person families are key drivers of average neighbourhood income throughout Toronto. This implies that focusing neighbourhood or business planning decisions on these types of families may help to increase a neighbourhood or business’ income position. Further, this analysis highlights that additional considerations for the unique characteristics of these key driver families are important to understand the interplay between families and neighbourhood income in more depth."
format: pdf
number-sections: true
bibliography: references.bib
---

@@

Following this, the variable of interest or the estimand within this analysis is the average neighbourhood income. As income can influence the kinds of opportunities and resources families in various neighbourhoods across Toronto have access to, this analysis seeks to better understand how neighbourhood average income levels are shaped by considering the impacts of different family sizes.
